Construction of Chebyshev nets with singularities

### 2017-09-12 Article.tex
changes

We consider a complete and simply connected immersed surface. Let 
$ D=[0,L_u]\Times[0,L_v],\quad\text{with } L_u,L_v\in\R_\ast^+$,
and let $\gamma_u:[0,L_u]\to\surf$ and $\gamma_v:[0,L_v]\to\surf$ be
 two curves such that $\gamma_u(0)=\gamma_v(0)$, and forming an
 interior angle $\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ at their
 intersection and exterior angle
 $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))$. For clarity of
 exposition, throughout this section, we consider a slightly different
 notion of Chebyshev net which will refer to mappings (not necessarily
 homeomorphisms) $\varphi:D\to\surf$ satisfying
\begin{subequations}\label{eq:cheb-def-c3}
\begin{align}\label{eq:cheb-def-c3a}
|\partial_u \varphi|_g(u,v) = 1,\\
|\partial_v \varphi|_g(u,v) = 1,\label{eq:cheb-def-c3b}
\end{align}
\end{subequations}
for all $(u,v)\in D$. Furthermore, note that the orientation of the boundary curve $\gamma_v$ is reversed in this section to simplify the exposition. 
We prove in the sequel the existence and the uniqueness of a Chebyshev net $\varphi:D\to\surf$ verifying the Cauchy boundary conditions
\begin{equation}\label{eq:cond-bord-c3}
\begin{split}
  \varphi(u,0)=\gamma_u(u),\quad\forall u\in[0,L_u],\\ 
  \varphi(0,v)=\gamma_v(v),\quad\forall v\in[0,L_v].
\end{split}
\end{equation}
Since $\surf$ is a plane immersion, and since $\int_\surf{K^+}<2\pi$
and $\int_\surf{K^-}<\infty$, there exists a global bi-Lipschitz
parametrization of $\surf$~\cite{Bonk03} and we identify
$\surf=(\R^2,g)$ such that there exists $\Csurf>1$ such that for all $X\in\R^2$,
\begin{equation}\label{eq:equiv}
  \frac{1}{\Csurf}|X|\leq |X|_{g} \leq \Csurf|X|.
\end{equation}

Following \cite{Ghys09}, we reformulate the problem of finding a Chebyshev net $\varphi:D\to\surf$ as the problem of finding the angle distribution $\omega:D\to(0,\pi)$ between the coordinate curves defined by $\omega(u,v) = \angle(\DU\varphi, \DV\varphi)(u,v)$. With this purpose in mind, we observe that $\omega$ satisfies the integrability condition (in the form of a modified Sine-Gordon equation) \cite{Ghys09}
\begin{equation}  \label{eq:cond-integr}
  \DUV \omega = -K(\varphi) \sin(\omega).
\end{equation}
Equivalently, $\omega$ satisfies the integrated form Gauss Bonnet formula of \eqref{eq:cond-integr} called the Hazzidakis formula
\begin{multline}  \label{eq:hazz-form}
 \omega(u,v) = \angle\big(\gamma_u'(0),\gamma_v'(0)\big) - \int_0^u \ko_u(s)ds +
  \int_{0}^v\ko_v(s)ds\\
 - \int_0^u\int_0^vK(\varphi(s,t))\sin\big[\omega(s,t)\big]ds~dt,
\end{multline} 
for all $(u,v)\in D$, with $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$ the geodesic curvatures of $\gamma_u$ and $\gamma_v$ respectively (see Figure \ref{fig:hazz-primal-c4}). 
\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=1cm,y=1cm]
    \pgfmathsetmacro{\cos}{cos(deg(60))}
    \pgfmathsetmacro{\sin}{sin(deg(60))}
    \draw[thick] (0,0) arc[start angle=150,delta angle=-30,radius=13.66] coordinate[pos=0.2] (u1) coordinate[pos=0.4] (u2) coordinate[pos=0.6] (u3) coordinate[pos=0.8] (u4);
    \coordinate (umid) at (2.3,2.7);
    \draw (umid) node[anchor=west]{$\varphi(\cdot,0){=}\gamma_u$};
    \draw[thick] (0,0) arc[start angle=-120,delta angle=-30,radius=13.66] coordinate[pos=0.2] (v1) coordinate[pos=0.4] (v2) coordinate[pos=0.6] (v3) coordinate[pos=0.8] (v4);
    \coordinate (vmid) at (-2.9,2.);
    \draw (vmid) node[anchor=east,inner sep=0pt]{$\varphi(0,\cdot){=}\gamma_v$};
   \draw[dotted] (u1) arc[start angle=-120,delta angle=-25,radius=13.66];
   \draw[dotted] (u2) arc[start angle=-120,delta angle=-20,radius=13.66];
   \draw[dotted] (u3) arc[start angle=-120,delta angle=-15,radius=13.66] coordinate[pos=0.8] (uv);
   \draw[dotted] (u4) arc[start angle=-120,delta angle=-10,radius=13.66];
   \draw[dotted] (v1) arc[start angle=150,delta angle=-25,radius=13.66];
   \draw[dotted] (v2) arc[start angle=150,delta angle=-20,radius=13.66];
   \draw[dotted] (v3) arc[start angle=150,delta angle=-15,radius=13.66];
   \draw[dotted] (v4) arc[start angle=150,delta angle=-10,radius=13.66];
   \draw[latex-] ($(uv)+(-42:0.5)$) arc[start angle=-42,delta angle=-96,radius=0.5];
   \draw ($(uv)+(-90:0.5)$) node[anchor=north]{$\omega(u,v)$};
 %   \draw[-latex] (0,0) -- (-30:1);
%    \draw ($(0,0)+(-45:0.4)$) node[anchor=north]{$\eta_1'(0)$};
 %   \draw[-latex] (0,0) -- (60:1);
%    \draw ($(0,0)+(130:0.9)$) node[anchor=west, inner sep=1pt]{$\eta_2'(0)$};
%    \draw[-latex] ($(0,0)+(-30:0.5)$) arc[start angle=-30, delta angle=90, radius=0.5];
%    \draw ($(0,0)+(15:0.5)$) node[anchor=west]{$\psi{=}\pi{-}\omega(0,0)$};
    \pgfmathsetmacro{\r}{0.5}
    \draw[-latex] (60:\r) arc[start angle=60, delta angle=90, radius=\r];
    \draw ($(90:.7)+(-.2,0)$) node{$\omega(0,0)$};
  \end{tikzpicture}
  \caption{Illustration of the coordinate curves of a Chebyshev net $\varphi$}\label{fig:hazz-primal-c4}
\end{figure}

@@

%We consider complete and simply connected surfaces $M$ with metric $g$. A Chebyshev net 
%$\varphi:U\subset\R^2\to\varphi(U)\subset\surf$, with $U$ an open set, is a coordinate system satisfying
%\begin{equation}\label{eq:cheb-def}
%  |\DU\varphi|_g(u,v) = |\DV\varphi|_g(u,v) = 1,
%\end{equation}
%for all $(u,v)\in U$.
%We construct in what follows Chebyshev nets with a finite set of conical singularities. 
%The main result is the following theorem.
%\begin{theorem}[Existence of piecewise smooth Chebyshev nets with singularities]\label{thm:existence-cheb-net}
%  Let $\surf$ be a smooth, complete, simply connected surface satisfying
%\begin{equation} \label{eq:cond-thm2}
%  \int_{\surf}K^+<2\pi\quad\text{and}\quad\int_{\surf}K^-<\infty,
%\end{equation}
%where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$. %We set $N_{\max} = \frac{4}{\pi}\int_\surf K^-+4$.
%Then, there exists a piecewise smooth Chebyshev net with conical singularities \sloppy$\CC=\big(\{\halfP^i_e\}_{1\leq i\leq \Npol}, \{\varphi^i_e\}_{1\leq i\leq \Npol}, T)$, with $\Npol\leq \frac{4}{\pi}\int_\surf K^-+8$, on $\surf$.
% $p_1,...,p_{\Nsing}$, with $\Nsing\leq N_{\max}$, of valence $n_1,...,n_{\Nsing}\in\{5,...,N_{\max}+4\}$ on $\surf$.
%\end{theorem}
%We highlight that the proof of the theorem is constructive. %Then, let us notice that the Chebyshev net with conical singularities constructed in Theorem \ref{thm:existence-cheb-net} induces a bi-Lipschitz mapping from the plane to $\surf$ \cite{Bur05}. As a result, this theorem is optimal for surfaces having a Gaussian curvature with constant sign \cite{Bonk03}.
%The section is organized as follows. In Section \ref{subsec:Nhalf-surfaces}, we first consider the construction of Chebyshev nets on broken half-surfaces, defined to be half-surfaces with polygonal boundaries. We prove the existence of Chebyshev nets on broken half-surfaces under some condition on their total curvature in Theorem \ref{thm:cheb-half-surface}. Then, we show in Section \ref{subsec:splitting} that we can split surfaces satisfying \eqref{eq:cond-thm} into broken half-surfaces (Theorem \ref{thm:splitting-surf}), each of them satisfying the conditions of Theorem \ref{thm:cheb-half-surface}. Finally, we combine these two results to construct the Chebyshev net with conical singularities in Section \ref{subsec:cheb-net-sing} and we show that this Chebyshev net is piecewise smooth.

 First, unless explicitly mentioned, any curve $\eta:I\subset \R\to\surf$ we consider in what follows is arc-length parametrized, continuous on $I$, and piecewise smooth according to the following definition:
\begin{definitionE}[Piecewise smooth curves]\label{def:piecewise}
  Let $\eta:I\subset \R\to\surf$ be a continuous curve. We say that the curve $\eta$ is \emph{piecewise smooth} if there exists a partition of $I$ in the form $\bigcup_{i=1}^{N+1} [a_{i-1},a_i]=I$, with $a_0<...<a_{N+1}$. Suppose moreover that $\eta$ restricted to $(a_{i-1},a_{i})$ is a smooth curve with all the derivatives having a finite limit from the right at $a_{i-1}$ and from the left at $a_{i}$, for all $i\in\{1,...,N+1\}$. We say that the curve $\eta$ is piecewise smooth.
\end{definitionE}
 We denote $\angle(X,Y)\in(-\pi,\pi]$ the oriented angle (using the orientation of $\surf$) between the vectors $X$ and $Y$ in the tangent plane $T_p\surf$ at any point $p\in\surf$. We define the total positive and negative turn angle of continuous piecewise smooth curves (see \cite{Bur05}):
\begin{definitionE}[Positive and negative turn angle $\tau_\pm$]
 Let $\eta:I\subset\R\to\surf$ be a continuous piecewise smooth curve on the partition of $I$ defined by $a_0<...<a_{N+1}$. Then, for all $i\in\{1,...,N+1\}$, let $\ko_i:[a_{i-1},a_{i}]\to\R$ be the geodesic curvature of $\eta\big|_{[a_{i-1},a_{i}]}$ defined by 
\begin{equation*}
  \ko_i(s) = \langle \eta^{\prime\prime}(s), \eta^{\prime\perp}(s)\rangle_g,
\end{equation*}
with $\eta^{\prime\perp}(s)\in T_{\eta(s)}\surf$ the vector such that $\angle(\eta'(s),\eta^{\prime\perp}(s))=\frac{\pi}{2}$, for all $s\in [a_{i-1},a_{i}]$.
Let $\psi_i = \angle(\eta'(a_i^-),\eta'(a_i^+))$, for all $i\in\{1,...,N\}$. We suppose that $-\pi<\psi_i<\pi$, for all $i\in\{1,...,N\}$. We define the total positive and negative \emph{turn angles} $\tau(\eta)$ by
\begin{equation}\label{eq:int-curv}
\tau_+(\eta) = \sum_{i=1}^{N+1}\int_{a_{i-1}}^{a_{i}}\ko_i^+ + \sum_{i=1}^N\psi_i^+,
\quad \tau_-(\eta) = \sum_{i=1}^{N+1}\int_{a_{i-1}}^{a_{i}}\ko_i^- + \sum_{i=1}^N\psi_i^-,
\end{equation}
and we define the total \emph{turn angle} as $\tau(\eta) = \tau_+(\eta)-\tau_-(\eta)$. (Note that $\tau_{\pm}(\eta)$ are different from $(\tau(\eta))^\pm$.) We denote $\tau\big(\eta\big|_{[a,b]})$, with $a,b\in\R$ such that $a<b$, the restriction to $[a,b]$ of the total turn angle. Note that, if any, the pointwise turns at $a$ and $b$ are included.
\end{definitionE}
An illustration of the turn angle is presented in Figure \ref{fig:turn-angle}. Finally, we denote int($D$) the interior of any set $D$. 
\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=2.cm,y=2.cm]
    \pgfmathsetmacro{\RR}{1.5}
    \pgfmathsetmacro{\del}{.5}
    \pgfmathsetmacro{\th}{30}
    \pgfmathsetmacro{\thh}{130}
    \begin{scope}[rotate=-90]
    \coordinate (A) at (0,0);
    \draw (A) -- ++(\th:\RR+1.) coordinate (B);
    \draw[thick,red,->] (A) -- ++(\th:.3);
    \draw (B) arc[start angle=-40,delta angle=60,radius=1.5] coordinate (C);
    \draw (C) -- ++(\thh:\RR) coordinate (D);
    \draw (D) -- ++(150:\RR) coordinate (E);

@@

%--------------------------------------------------------------------
%
%Before proving this result, we recall a theorem proved in Section \ref{sec:chap4}.
%\begin{theorem}[Existence of a unique solution to integrability condition]\label{thm:exist-cond-integr-c5}
%Let $\surf$ be a smooth, open, complete, and simply connected surface. Let $\eta_1:\R^-\to\surf$ and $\eta_2:\R^+\to\surf$ be two smooth curves with respective geodesic curvatures $\ko_1:\R^-\to\R$ and $\ko_2:\R^+\to\R$, and such that $\eta_1(0) = \eta_2(0)$. Suppose that $\psi:=\angle(\eta_1'(0),\eta_2'(0))\in(0,\pi)$. Then, there exists a unique angle distribution $\omega:(\R^+)^2\to\R/2\pi\Z$ satisfying the Hazzidakis formula \eqref{eq:hazz2-c4}, with $\varphi:(\R^+)^2\to\surf$ the unique smooth mapping satisfying the boundary conditions \eqref{eq:bound-cond-c4}, and such that its $v$-coordinate curves are arc-length parametrized curves with a geodesic curvature $\kop_2:D\to\R$ satisfying $\kop_2(u,v) = \DV\omega(u,v)$, for all $(u,v)\in (\R^+)^2$.
%
%Suppose moreover that there exists $\tilde D=[0,\tilde L_2]\Times[0,\tilde L_1]$, with $\tilde L_1,\tilde L_2\in\R^+_\ast$, such that $0<\omega(u,v)<\pi$, for all $(u,v)\in \tilde D$. Then, the mapping $\varphi$ satisfies 
%\begin{equation}\label{eq:def-cheb3-c5}
%  |\DU\varphi|_g(u,v) = |\DV\varphi|_g(u,v)=1,
%\end{equation}
%for all $(u,v)\in \tilde D$.
%\end{theorem}
%\begin{proof}[Proof of Proposition \ref{prop:sector}]
%  Using Theorem \ref{thm:exist-cond-integr-c5}, we infer that there exists a unique angle distribution $\omega:(\R^+)^2\to\R/2\pi\Z$ satisfying the Hazzidakis formula \eqref{eq:hazz2-c4}, with $\varphi:(\R^+)^2\to\surf$ the unique mapping satisfying the boundary conditions \eqref{eq:bound-cond-c4} and the properties presented in the theorem.
%Then, using the continuity of the angle distribution $\omega$ and $\omega(0,0)=\pi-\psi\in(0,\pi)$, we infer that there exists $\tilde L_1,\tilde L_2>0$ such that $\omega(u,v)\in(0,\pi)$ for all $(u,v)\in[0,\tilde L_1]\Times[0,\tilde L_2]$. Hence, by Theorem \ref{thm:exist-cond-integr-c5}, the mapping $\varphi$ satisfies \eqref{eq:def-cheb3-c5} for all $(u,v)\in[0,\tilde L_1]\Times[0,\tilde L_2]$. Then, in the same manner as in the proof of Lemma \ref{lem:homeo}, we obtain that $\varphi:(\R^+)^2\to\sect$ is a Chebyshev net. Suppose finally that $\tilde\varphi:(\R^+)^2\to\surf$ is a Chebyshev net satisfying the boundary conditions \eqref{eq:bound-cond-c4}. Then, using Property \ref{prop:hazz-form}, we obtain that the angle distribution $\tilde\omega:(\R^+)^2\to(0,\pi)$ defined by $\tilde\omega=\angle(\DU\tilde\varphi,\DV\tilde\varphi)(u,v)$, for all $(u,v)\in(\R^+)^2$, satisfies the Hazzidakis formula \eqref{eq:hazz2-c4}. We deduce from Theorem \ref{thm:exist-cond-integr-c5} that $\varphi=\tilde\varphi$. This concludes the proof.
%\end{proof}
-------------------------------------------------------------------------------------------------
\section{Construction of a Chebyshev net from its angle distribution}\label{subsec:constr-param}

>>>>

We consider $M$ complete and simply connected immersed surfaces. 
In a first part we will be interested in the construction of T-net in a sector
of $M$ bounded by two half line. More precisely, let $L_u,L_v\in\R_\ast^+$ and
$\gamma_u:[0,L_u]\to\surf$ and $\gamma_v:[0,L_v]\to\surf$ be
 two curves  such that $\gamma_u(0)=\gamma_v(0)$, and forming an
 interior angle $\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ at their
 intersection and exterior angle $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))$.

We consider a slightly different notion of Chebyshev net which will refer to mappings (not necessarily
 homeomorphisms) $\varphi: D=[0,L_u]\Times[0,L_v] \to\surf$ satisfying
\begin{subequations}\label{eq:cheb-def-c3}
\begin{align}\label{eq:cheb-def-c3a}
|\partial_u \varphi|_g(u,v) = 1,\\
|\partial_v \varphi|_g(u,v) = 1,\label{eq:cheb-def-c3b}
\end{align}
\end{subequations}
for all $(u,v)\in D$.

{\bf  ""Furthermore, note that the orientation of the boundary curve $\gamma_v$ is reversed in this section to simplify the exposition."" ???}

We prove in the sequel the existence and the uniqueness of a Chebyshev net $\varphi:D\to\surf$ verifying the Cauchy boundary conditions
\begin{equation}\label{eq:cond-bord-c3}
\begin{split}
  \varphi(u,0)=\gamma_u(u),\quad\forall u\in[0,L_u],\\ 
  \varphi(0,v)=\gamma_v(v),\quad\forall v\in[0,L_v].
\end{split}
\end{equation}
In the following, $\surf$ is a finite total curvature immersed plane with $\int_\surf{K^+}<2\pi$
and $\int_\surf{K^-}<\infty$. Hence there exists a global bi-Lipschitz
parametrization $F: \R^2 \to \surf$~\cite{Bonk03} and if $g$ is the induced metric,
for all $X\in\R^2$ there exists $\Csurf>1$ such that
\begin{equation}\label{eq:equiv}
  \frac{1}{\Csurf}|X|\leq |X|_{g} \leq \Csurf|X|.
\end{equation}

Following \cite{Ghys09}, we reformulate the problem of finding a Chebyshev net $\varphi:D\to\surf$ as the problem of finding the angle distribution $\omega:D\to(0,\pi)$ between the coordinate curves defined by $\omega(u,v) = \angle(\DU\varphi, \DV\varphi)(u,v)$. With this purpose in mind, we observe that $\omega$ satisfies the integrability condition (in the form of a modified Sine-Gordon equation) \cite{Ghys09}
\begin{equation}  \label{eq:cond-integr}
  \DUV \omega = -K(\varphi) \sin(\omega).
\end{equation}
Equivalently, $\omega$ satisfies the integrated form Gauss Bonnet formula of \eqref{eq:cond-integr} called the Hazzidakis formula

{\bf  Signes de la formule et conventions de signes du parametrage}
\begin{multline}  \label{eq:hazz-form}
 \omega(u,v) = \angle\big(\gamma_u'(0),\gamma_v'(0)\big) - \int_0^u \ko_u(s)ds +
  \int_{0}^v\ko_v(s)ds\\
 - \int_0^u\int_0^vK(\varphi(s,t))\sin\big[\omega(s,t)\big]ds~dt,
\end{multline} 
for all $(u,v)\in D$, with $\ko_u:[0,L_u]\to\R$ and $\ko_v:[0,L_v]\to\R$ the geodesic curvatures of $\gamma_u$ and $\gamma_v$ respectively (see Figure \ref{fig:hazz-primal-c4}).

\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=1cm,y=1cm]
    \pgfmathsetmacro{\cos}{cos(deg(60))}
    \pgfmathsetmacro{\sin}{sin(deg(60))}
    \draw[thick] (0,0) arc[start angle=150,delta angle=-30,radius=13.66] coordinate[pos=0.2] (u1) coordinate[pos=0.4] (u2) coordinate[pos=0.6] (u3) coordinate[pos=0.8] (u4);
    \coordinate (umid) at (2.3,2.7);
    \draw (umid) node[anchor=west]{$\varphi(\cdot,0){=}\gamma_u$};
    \draw[thick] (0,0) arc[start angle=-120,delta angle=-30,radius=13.66] coordinate[pos=0.2] (v1) coordinate[pos=0.4] (v2) coordinate[pos=0.6] (v3) coordinate[pos=0.8] (v4);
    \coordinate (vmid) at (-2.9,2.);
    \draw (vmid) node[anchor=east,inner sep=0pt]{$\varphi(0,\cdot){=}\gamma_v$};
   \draw[dotted] (u1) arc[start angle=-120,delta angle=-25,radius=13.66];
   \draw[dotted] (u2) arc[start angle=-120,delta angle=-20,radius=13.66];
   \draw[dotted] (u3) arc[start angle=-120,delta angle=-15,radius=13.66] coordinate[pos=0.8] (uv);
   \draw[dotted] (u4) arc[start angle=-120,delta angle=-10,radius=13.66];
   \draw[dotted] (v1) arc[start angle=150,delta angle=-25,radius=13.66];
   \draw[dotted] (v2) arc[start angle=150,delta angle=-20,radius=13.66];
   \draw[dotted] (v3) arc[start angle=150,delta angle=-15,radius=13.66];
   \draw[dotted] (v4) arc[start angle=150,delta angle=-10,radius=13.66];
   \draw[latex-] ($(uv)+(-42:0.5)$) arc[start angle=-42,delta angle=-96,radius=0.5];
   \draw ($(uv)+(-90:0.5)$) node[anchor=north]{$\omega(u,v)$};
 %   \draw[-latex] (0,0) -- (-30:1);
%    \draw ($(0,0)+(-45:0.4)$) node[anchor=north]{$\eta_1'(0)$};
 %   \draw[-latex] (0,0) -- (60:1);
%    \draw ($(0,0)+(130:0.9)$) node[anchor=west, inner sep=1pt]{$\eta_2'(0)$};
%    \draw[-latex] ($(0,0)+(-30:0.5)$) arc[start angle=-30, delta angle=90, radius=0.5];
%    \draw ($(0,0)+(15:0.5)$) node[anchor=west]{$\psi{=}\pi{-}\omega(0,0)$};
    \pgfmathsetmacro{\r}{0.5}
    \draw[-latex] (60:\r) arc[start angle=60, delta angle=90, radius=\r];
    \draw ($(90:.7)+(-.2,0)$) node{$\omega(0,0)$};
  \end{tikzpicture}
  \caption{Illustration of the coordinate curves of a Chebyshev net $\varphi$}\label{fig:hazz-primal-c4}
\end{figure}

@@

%We construct in a second part Chebyshev nets with a finite set of conical singularities on surfaces with finite total 
%negative curvature and total positive curvature lower than $2\pi$. The main result of this section is the following theorem.
%\begin{theorem}[Existence of piecewise smooth Chebyshev nets with singularities]\label{thm:existence-cheb-net}
%  Let $\surf$ be a smooth, complete, simply connected surface satisfying
%\begin{equation} \label{eq:cond-thm2}
%  \int_{\surf}K^+<2\pi\quad\text{and}\quad\int_{\surf}K^-<\infty,
%\end{equation}
%where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$. %We set $N_{\max} = \frac{4}{\pi}\int_\surf K^-+4$.
%Then, there exists a piecewise smooth Chebyshev net with conical singularities \sloppy$\CC=\big(\{\halfP^i_e\}_{1\leq i\leq \Npol}, \{\varphi^i_e\}_{1\leq i\leq \Npol}, T)$, with $\Npol\leq \frac{4}{\pi}\int_\surf K^-+8$, on $\surf$.
% $p_1,...,p_{\Nsing}$, with $\Nsing\leq N_{\max}$, of valence $n_1,...,n_{\Nsing}\in\{5,...,N_{\max}+4\}$ on $\surf$.
%\end{theorem}
%We highlight that the proof of the theorem is constructive. %Then, let us notice that the Chebyshev net with conical singularities constructed in Theorem \ref{thm:existence-cheb-net} induces a bi-Lipschitz mapping from the plane to $\surf$ \cite{Bur05}. As a result, this theorem is optimal for surfaces having a Gaussian curvature with constant sign \cite{Bonk03}.
%The section is organized as follows. In Section \ref{subsec:Nhalf-surfaces}, we first consider the construction of Chebyshev nets on broken half-surfaces, defined to be half-surfaces with polygonal boundaries. We prove the existence of Chebyshev nets on broken half-surfaces under some condition on their total curvature in Theorem \ref{thm:cheb-half-surface}. Then, we show in Section \ref{subsec:splitting} that we can split surfaces satisfying \eqref{eq:cond-thm} into broken half-surfaces (Theorem \ref{thm:splitting-surf}), each of them satisfying the conditions of Theorem \ref{thm:cheb-half-surface}. Finally, we combine these two results to construct the Chebyshev net with conical singularities in Section \ref{subsec:cheb-net-sing} and we show that this Chebyshev net is piecewise smooth.

In a second part, we will apply the construction on sectors to consider the case where the boundary curve of the sector $\eta:I\subset \R\to\surf$ we consider is arc-length parametrized, continuous on $I$, and piecewise smooth according to the following definition:
\begin{definitionE}[Piecewise smooth curves]\label{def:piecewise}
  Let $\eta:I\subset \R\to\surf$ be a continuous curve. We say that the curve $\eta$ is \emph{piecewise smooth} if there exists a partition of $I$ in the form $\bigcup_{i=1}^{N+1} [a_{i-1},a_i]=I$, with $a_0<...<a_{N+1}$. Suppose moreover that $\eta$ restricted to $(a_{i-1},a_{i})$ is a smooth curve with all the derivatives having a finite limit from the right at $a_{i-1}$ and from the left at $a_{i}$, for all $i\in\{1,...,N+1\}$. We say that the curve $\eta$ is piecewise smooth.
\end{definitionE}
We define the total positive and negative turn angle of continuous piecewise smooth curves (see \cite{Bur05}):
\begin{definitionE}[Positive and negative turn angle $\tau_\pm$]
 Let $\eta:I\subset\R\to\surf$ be a continuous piecewise smooth curve on the partition of $I$ defined by $a_0<...<a_{N+1}$. Then, for all $i\in\{1,...,N+1\}$, let $\ko_i:[a_{i-1},a_{i}]\to\R$ be the geodesic curvature of $\eta\big|_{[a_{i-1},a_{i}]}$ defined by 
\begin{equation*}
  \ko_i(s) = \langle \eta^{\prime\prime}(s), \eta^{\prime\perp}(s)\rangle_g,
\end{equation*}
with $\eta^{\prime\perp}(s)\in T_{\eta(s)}\surf$ the vector such that $\angle(\eta'(s),\eta^{\prime\perp}(s))=\frac{\pi}{2}$, for all $s\in [a_{i-1},a_{i}]$.
Let $\psi_i = \angle(\eta'(a_i^-),\eta'(a_i^+))$, for all $i\in\{1,...,N\}$. We suppose that $-\pi<\psi_i<\pi$, for all $i\in\{1,...,N\}$. We define the total positive and negative \emph{turn angles} $\tau(\eta)$ by
\begin{equation}\label{eq:int-curv}
\tau_+(\eta) = \sum_{i=1}^{N+1}\int_{a_{i-1}}^{a_{i}}\ko_i^+ + \sum_{i=1}^N\psi_i^+,
\quad \tau_-(\eta) = \sum_{i=1}^{N+1}\int_{a_{i-1}}^{a_{i}}\ko_i^- + \sum_{i=1}^N\psi_i^-,
\end{equation}
and we define the total \emph{turn angle} as $\tau(\eta) = \tau_+(\eta)-\tau_-(\eta)$. (Note that $\tau_{\pm}(\eta)$ are different from $(\tau(\eta))^\pm$.) We denote $\tau\big(\eta\big|_{[a,b]})$, with $a,b\in\R$ such that $a<b$, the restriction to $[a,b]$ of the total turn angle. Note that, if any, the pointwise turns at $a$ and $b$ are included.
\end{definitionE}
An illustration of the turn angle is presented in Figure \ref{fig:turn-angle}. Finally, we denote int($D$) the interior of any set $D$.

\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=2.cm,y=2.cm]
    \pgfmathsetmacro{\RR}{1.5}
    \pgfmathsetmacro{\del}{.5}
    \pgfmathsetmacro{\th}{30}
    \pgfmathsetmacro{\thh}{130}
    \begin{scope}[rotate=-90]
    \coordinate (A) at (0,0);
    \draw (A) -- ++(\th:\RR+1.) coordinate (B);
    \draw[thick,red,->] (A) -- ++(\th:.3);
    \draw (B) arc[start angle=-40,delta angle=60,radius=1.5] coordinate (C);
    \draw (C) -- ++(\thh:\RR) coordinate (D);
    \draw (D) -- ++(150:\RR) coordinate (E);

@@

%--------------------------------------------------------------------
%
%Before proving this result, we recall a theorem proved in Section \ref{sec:chap4}.
%\begin{theorem}[Existence of a unique solution to integrability condition]\label{thm:exist-cond-integr-c5}
%Let $\surf$ be a smooth, open, complete, and simply connected surface. Let $\eta_1:\R^-\to\surf$ and $\eta_2:\R^+\to\surf$ be two smooth curves with respective geodesic curvatures $\ko_1:\R^-\to\R$ and $\ko_2:\R^+\to\R$, and such that $\eta_1(0) = \eta_2(0)$. Suppose that $\psi:=\angle(\eta_1'(0),\eta_2'(0))\in(0,\pi)$. Then, there exists a unique angle distribution $\omega:(\R^+)^2\to\R/2\pi\Z$ satisfying the Hazzidakis formula \eqref{eq:hazz2-c4}, with $\varphi:(\R^+)^2\to\surf$ the unique smooth mapping satisfying the boundary conditions \eqref{eq:bound-cond-c4}, and such that its $v$-coordinate curves are arc-length parametrized curves with a geodesic curvature $\kop_2:D\to\R$ satisfying $\kop_2(u,v) = \DV\omega(u,v)$, for all $(u,v)\in (\R^+)^2$.
%
%Suppose moreover that there exists $\tilde D=[0,\tilde L_2]\Times[0,\tilde L_1]$, with $\tilde L_1,\tilde L_2\in\R^+_\ast$, such that $0<\omega(u,v)<\pi$, for all $(u,v)\in \tilde D$. Then, the mapping $\varphi$ satisfies 
%\begin{equation}\label{eq:def-cheb3-c5}
%  |\DU\varphi|_g(u,v) = |\DV\varphi|_g(u,v)=1,
%\end{equation}
%for all $(u,v)\in \tilde D$.
%\end{theorem}
%\begin{proof}[Proof of Proposition \ref{prop:sector}]
%  Using Theorem \ref{thm:exist-cond-integr-c5}, we infer that there exists a unique angle distribution $\omega:(\R^+)^2\to\R/2\pi\Z$ satisfying the Hazzidakis formula \eqref{eq:hazz2-c4}, with $\varphi:(\R^+)^2\to\surf$ the unique mapping satisfying the boundary conditions \eqref{eq:bound-cond-c4} and the properties presented in the theorem.
%Then, using the continuity of the angle distribution $\omega$ and $\omega(0,0)=\pi-\psi\in(0,\pi)$, we infer that there exists $\tilde L_1,\tilde L_2>0$ such that $\omega(u,v)\in(0,\pi)$ for all $(u,v)\in[0,\tilde L_1]\Times[0,\tilde L_2]$. Hence, by Theorem \ref{thm:exist-cond-integr-c5}, the mapping $\varphi$ satisfies \eqref{eq:def-cheb3-c5} for all $(u,v)\in[0,\tilde L_1]\Times[0,\tilde L_2]$. Then, in the same manner as in the proof of Lemma \ref{lem:homeo}, we obtain that $\varphi:(\R^+)^2\to\sect$ is a Chebyshev net. Suppose finally that $\tilde\varphi:(\R^+)^2\to\surf$ is a Chebyshev net satisfying the boundary conditions \eqref{eq:bound-cond-c4}. Then, using Property \ref{prop:hazz-form}, we obtain that the angle distribution $\tilde\omega:(\R^+)^2\to(0,\pi)$ defined by $\tilde\omega=\angle(\DU\tilde\varphi,\DV\tilde\varphi)(u,v)$, for all $(u,v)\in(\R^+)^2$, satisfies the Hazzidakis formula \eqref{eq:hazz2-c4}. We deduce from Theorem \ref{thm:exist-cond-integr-c5} that $\varphi=\tilde\varphi$. This concludes the proof.
%\end{proof}

\section{Construction of a Chebyshev net from its angle distribution}\label{subsec:constr-param}
We now prove that a Chebyshev net can be constructed uniquely from its angle distribution. We start by showing in Subsection \ref{subsec:construction} that the construction of curves from their geodesic curvature, initial point and initial tangent vector is a well-posed problem. We then define, following \cite{Ghys09}, the mapping $\I(\gamma,\omega)$ which, for given boundary curves $\gamma_u$ and $\gamma_v$, associates with any angle distribution $\omega$ satisfying the boundary conditions \eqref{eq:cond-bord-angle} the candidate Chebyshev net $\varphi$, with angle distribution $\omega$, satisfying the boundary conditions \eqref{eq:cond-bord-c3} (Subsection \ref{subsubsec:constr-param}). The parametrization $\varphi$ is constructed in such a way that the $v$-coordinate curves are arc-length parametrized curves with geodesic curvatures satisfying \eqref{eq:courb-geodb}. We moreover show the continuity of the mapping $\I$ with respect to the angle distribution and to the delimiting curves $\gamma_u$ and $\gamma_v$. In Subsection \ref{sec:reg-candidate}, we show that the candidate Chebyshev net $\varphi$ has improved regularity in the $u$-coordinate whenever $\omega$ satisfies the integrability condition \eqref{eq:cond-integr}. Finally, in Subsection \ref{sec:reg-cheb}, we prove that $\varphi$ is indeed a Chebyshev net if $\omega$ satisfies the integrability condition and has a sufficient regularity.
